Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
described Threats to validity section
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

@@

\textcolor{red}{Lucas: describe here the threats to validity}

>>>>

The median run-time for our benchmark set is 6.6\,s for fixed-point and 5.45\,s for floating-point. 
We consider these times short enough to be of practical use to control engineers, and thus affirm EG1.

There are a few instances for which the system fails to find a controller. 
For the na\"ive approach, the completeness threshold may be too large, thus
causing a timeout.  On the other hand, the abstraction-based approach may
require a very precise abstraction, resulting in too many refinements and,
consequently, in a timeout.  Yet another source of incompleteness is the
inability of the {\sc synthesize} phase to use a large enough precision for
the plant model.

@@

\textit{Benchmark selection:} We report an assessment of both our approaches
over a diverse set of real-world benchmarks.  Nevertheless, this set of
benchmarks is limited within the scope of this paper and the performance may
not generalize to other benchmarks.\\
%
\textit{Plant precision and discretization heuristics:} Our algorithm to
select suitable FWL word widths to model the plant behavior 
increases the precision by 8 bits at each step 
in order to be compliant with the CBMC type API. 
Similarly, for discretization, we run multiple discretizations for each
benchmark and retain the fastest run.
This works sufficiently well for our benchmarks, but
performance may suffer in some cases, for example if the completeness
threshold is high.\\
%
\textit{Abstraction on other properties:} The performance gain from abstract
acceleration may not hold for more complex properties than safety, for
instance ``eventually reach and always remain in a given safe set''.
